\documentclass[12pt]{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}

\begin{document}
	
	\begin{letter}{Editor-in-Chief of the Thoery \& Methodology Section\\ Psychometrika}
		
		\opening{Dear Theory \& Methodology Editors,}
		
		My co-authors and I are enclosing a submission entitled ``New Item Response Theory-based Algorithms for the Development of Short Test Forms'' for consideration in the Theory \& Methodology section of Psychometrika. 
		This manuscript presents novel methodologies grounded in Item Response Theory for constructing short test forms while maintaining psychometric integrity. The study contributes to the literature by introducing efficient algorithms that optimize item selection based on theoretical and empirical considerations.
		
		The manuscript is 22 pages long, including the title page, figures, tables, and references. We affirm that this work has not been published previously and is not under consideration for publication elsewhere. Additionally, all authors declare that there are no conflicts of interest to disclose.
		
		We believe that our findings will be of interest to researchers and practitioners in psychometrics, educational measurement, and related fields. We appreciate your time and consideration and look forward to your feedback.
		
		
		The manuscript has not be submitted elsewhere. 
		
		The authors have no conflict of interest to disclose.
		
		
			Please do not hesitate to contact me should you require any further information.
%		\closing{Sincerely,\\ Your Name\\ Your Affiliation\\ Your Email Address\\ Your Corresponding Address}
		
	\end{letter}
	
\end{document}